Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-09-15 WSSSPE4_report/WSSSPE4_report.tex
added descriptions of the two tracks

\begin{quote}
    call for participation
\end{quote}

>>>>

\begin{quote}
    \textbf{Track 1 -- Building a sustainable future for open-use research
    software} has the goals of defining a vision of the future of open-use
    research software, and in the workshop, initiating the activities that are
    needed to get there. The idea of this track is to first think about where
    we want to be 5 to 10 years from now, without being too concerned with
    where we are today, and then to determine how we can move to this future.

    \textbf{Track 2 -- Practices \& experiences in sustainable scientific software}
    has the goal of improving the quality of today's research software and the
    experiences of its developers by sharing practices and experiences.
    This track is focused on the current state of scientific software and what
    we can do to improve it in the short term, starting with where we are today.
\end{quote}
